---
title: 'iMRMC estimation of sensitivity and specificity '
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(pander)
knitr::opts_chunk$set(echo = TRUE)
```

The software can estimate sensitivity and specificity. However, the key is to format the data as the input file. The first 3 columns are the same as the input for AUC analysis of ROC data. The last column now represents the zero-one (negative-positive) binary decision.  

##Transform iMRMC input file for Sensitivity or Specificity Analysis
###1.	Do not need to edit truth data

###2.	Edit score data
```{r EditScore, echo=FALSE}
EditScoreDataDf = data.frame(AnalysisPurposes = c('Sensitivity','Sensitivity','Sensitivity','Specificity','Specificity','Specificity'),
                           CaseTruth = c('Disease case','Disease case','Non-Disease case','Disease case','Non-Disease case','Non-Disease case'),
                           ReaderDecision = c('Disease (score>threshold)','Non-disease (score<threshold)','Does not matter','Does not matter','Disease (score>threshold)','Non-disease (score<threshold)'),
                           BinaryDecision = c(1,0,0.5,0.5,1,0))

pander(EditScoreDataDf, type = 'grid')

```

###3. Example
Calculate pathologists’ sensitivity for dataset A

  For disease cases, if reader’s score is larger than or equal to the threshold (≥3), set the last column for that reader and case to 1 (e.g. since reader2 gave score 4 to case3, set the last column of this row to 1)

  For disease cases, if reader’s score is lower than threshold (<3), set the last column for that reader and case to 0 (e.g. since reader11 gave score 1 to case3, set the last column of this row to 0)

  Set all scores (last column) for non-diseases cases to 0.5 (e.g. since case1 is non-disease case, set last column for case1 from all readers to 0.5).

