---
title: "Simulate MRMC Data"
output:
  pdf_document: default
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
library(knitr)
library(iMRMC)
knitr::opts_chunk$set(echo = TRUE)
```

There are two functions in this package that can simulate Multi-reader Multi-case (MRMC) data. sim.NormalIG.Hierarchical is the function to simulate the MRMC agreement data with no binary truth state. The sim.gRoeMetz is the function to simulate MRMC ROC data.

## 1. Using the new hierachical model to simulate the MRMC agreement data

The following is how to use the sim.NormalIG.Hierachcial.R to simulate MRMC data with no truth state, the MRMC agreement data

```{r}

# configuration
nR = 5       #number of readers
nC = 100     #number of cases

config <- sim.NormalIG.Hierarchical.config(nR=nR, nC=nC, modalityID = c("testA","testB")) 

# simulate MRMC study
set.seed(1, kind = "L'Ecuyer-CMRG")
dFrame.newH <- sim.NormalIG.Hierarchical(config)

# check the first and last few lines of the simulated dataframe
head(dFrame.newH)
tail(dFrame.newH)
```

We simulated 5 readers and 100 cases for 2 modalities, so the total number of scores is 5x100x2=1000.

## 2. Using sim.gRoeMetz in iMRMC package to simulate MRMC ROC data

The following is how to use the sim.gRoeMetz.R to simulate MRMC data with truth state, the MRMC ROC data

```{r}

# configuration
nR = 5       #number of readers
nC.neg = 50  #number of positive cases
nC.pos = 50  #number of negative cases

config <- sim.gRoeMetz.config(nR = nR, nC.neg = nC.neg, nC.pos = nC.neg)

# simulate MRMC study
set.seed(1, kind = "L'Ecuyer-CMRG")
dFrame.gRM <- sim.gRoeMetz(config)

# check the first and last few lines of the simulated dataframe
head(dFrame.gRM)
tail(dFrame.gRM)
```

The simulated data starts with truth state of each case, and followed by the reading scores from each of the readers. Since we simulate 50 positive cases and 50 negative cases, there are 100 lines for the truth and 100x5x2 = 1000 lines for the scores from 5 readers for 2 modalities.

To combine the truth data and the reader scores and change the data to a dataframe with 5 columns: readerID, caseID, modalityID, score, truth, we can use the function undoIMRMCdf in iMRMC pacakge:
```{r}
dFrame.gRM.2 <- undoIMRMCdf(dFrame.gRM)

# check the first and last few lines of the simulated dataframe
head(dFrame.gRM.2)
tail(dFrame.gRM.2)
```
